Deliminative verbal reduplication in Mandarin Chinese

### 2024-09-06 replies-reviews.tex

Thank you very much for the positive reviews. The following text is a repetition of the points the
reviewers raised and an explanation of how we addressed open issues.

\section{Reviewer 1}\label{sec:1}

\begin{enumerate}
%%%%% YL
\item
Regarding the interaction with Aktionsart (Sec. 2.3.2), the author(s) conclude(s) that ``This shows
that although the reduplication does have a tendency to interact with volitional verbs and with
activities and semelfactives due to its dynamic meaning, this is by no means a rigid constraint, and
non-volitional verbs, states and achievements can be reduplicated in appropriate contexts as well.''

Regarding volitionality, it should be noted that, as reported in various grammars, while it is generally true that verbs describing events not controlled by an agent cannot be reduplicated, some of them, under certain circumstances (e.g. in imperative or conditional sentences, or in causative \obj{rang4/jiao4/shi3} sentences, as in ex. (15e) provided by the author(s)), can reduplicate (it might be worthwhile to delve into why this occurs in such sentence structures). As for the possibility of reduplicating stative verbs, this is limited to specific verbs and circumstances. It has been observed that some stative verbs, e.g. \obj{bing4} ‘be sick’, are basically change of state predicates, which means that they are dynamic (see e.g. \citealt[663]{Tham2013}; see also \citealt{Sybesma1997, Liu2010, PeckEtAl2013, Basciano2019}). The same goes for those verbs expressing psychological states which can have a dynamic interpretation, as e.g. \obj{liao3jie3} `understand' \citep[fn. 3]{BascianoMelloni2017}. 
With regard to achievements, it is worth considering whether, in certain circumstances (the cases in which they are reduplicated), they assume a reading that cancels the \textit{telos}. Anyway, since these cases are not the rule, I do not think they can be taken as an argument against the constraints on the action type of the base verb. Otherwise, if reduplication does not affect lexical aspect, how can the changes in the aspect properties of the verb after reduplication be explained? (e.g. 看（了）三个小时 \obj{kan4} \obj{(le)} \obj{san1} \obj{ge} \obj{xiao3shi2} `read for three hours' vs. *看（了）看三个小时 \obj{kan4} \obj{(le)} \obj{kan4} \obj{san1} \obj{ge} \obj{xiao3shi2} (both reduplication and for X time expressions set a boundary to the event) / 正在看 \obj{zheng4zai4} \obj{kan4} / *正在看看 \obj{zheng4zai4} \obj{kan4} \obj{kan}).

In order to get a clearer picture and to find a semantic explanation for these facts, one should look at what these ‘special’ cases of reduplication have in common and try to draw generalizations: why can some stative and achievement verbs reduplicate under certain circumstances, while other cannot? What do these verbs have in common? Can we single out specific subclasses of these verbs which can reduplicate?

@@

Due to its unique features compared to the perfective aspect marker \obj{le} and the experiential aspect marker \obj{guo4},
the reduplication is the only perfective viewpoint aspect that can freely occur in future situations \citep[156--157]{XiaoMcEnery2004}.
\textit{Le} expresses a situation being realized,
while \textit{guo4} conveys a situation already experienced,
and thus, both rarely occur in future situations.
The use of reduplication does not have these constraints.
This explains the general tendency for the reduplication to appear in conditional clauses and imperative or causative contexts,
which are frequently used to describe future situations.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
%%%%% YL
\item
The author(s) argue(s) that verbal reduplication is a morphological phenomenon based on some tests (Sect. 2.4). However, the tests used have some shortcomings.

1) Compositionality: this test is not reliable. There are phrases whose meaning is not

compositional (see e.g. \textit{kick the bucket}, \textit{shoot the breeze}). Also, take verb-object constructions,
which are ambiguous between words and phrases: e.g. 担心 \obj{dan1-xin1} `take on-heart, worry' has a
non-compositional meaning, suggesting that it is a word, but is separable, suggesting that it is a
phrase (see \citealt{Huang1984}). 
On p. 14, the author(s) state(s): “The meaning of the reduplication is not
compositional, as it does not mean that the event denoted by the verb happens twice or multiple
times, but rather that the event happens for a short duration and/or for low frequency. This non-
compositionality suggests that a reduplication is more word-like.”

@@

If it were compositional, perhaps the meaning should be something like ‘look look” (do the action twice?) but not multiple times. However, I think it is a matter of iconicity rather than compositionality here. In addition, would this imply that the reduplicated verb is a compound? Its meaning and function, though, seem to be closer to inflection or derivation. If it is a derivational item, i.e. a suffix-like element, it can bear a fix aspectual meaning (delimitative aspect): in this sense, the meaning would be compositional.

2) Lexical integrity: if the reduplicated verb is a word, the position of the perfective aspect
marker le is unexpected. In fact, it is never found in between the two constituents of a compound
word, as the author(s) also show(s) in (27c). \citet[1282]{Her2006}, talking about V-给 \obj{gei3} sequences,
states that ``The simple fact that the V-gei sequence cannot be separated, as in (19c) indicates its
lexical integrity'', i.e. they form a single lexical item (寄给了他 \obj{ji4-gei3-le} \obj{ta1} vs. * 寄了给她 \obj{ji4-le} \obj{gei3} \obj{ta1}).
%\itdopt{St. Mü.: fix brackets and references to examples. The quoted text contains Chinese
%  characters. Please try to insert them. Also for the examples below.}
Even if you assume that aspect markers are suffixes (morphological elements), they should not be placed in between the constituents of compounds, because this violates lexical integrity (as shown in ex. 27b by the author(s)): the suffix \obj{le} must be placed after the whole complex verb, which forms a single lexical unit, and not within it. In fact, in (non-separable) verb-object compounds, which are lexical units, 了 \obj{le} is never placed after the verbal constituent (关心了 \obj{guan1-xin1-le} / *关了心 \obj{guan1-le} \obj{xin1} vs. 骑了马 \obj{qi2-le} \obj{ma3}).
It is worth noticing that, different from diminishing verb reduplication, in AABB verbal reduplication (which has a different meaning and function), the perfective aspect marker /e can never be placed inside the reduplicated verb but can be put at the end of the AABB pattern.

Also, I do not understand the comparison with SVCs. Let's say that reduplication is a syntactic phenomenon, but that does not mean that it is a SVC, i.e. a sequence of verbs or verb phrases in a relation of coordination or subordination, which are basically independent of each other. It could simply be another type of syntactic construction with its specific properties.

3) Phrasal substitution. The inclusion of this test is questionable since reduplication primarily targets verbs and not phrases. Therefore, syntactic objects should not be included in the reduplication; it is not repetition of phrases. Indeed, if the object is part of a non-separable verb-object compound (which is a lexical unit), it is included in the reduplication (关心关心 \obj{guan1-xin1} \obj{guan1-xin1}/*  关关心 \obj{guan1-guan1} \obj{xin1} vs. 跳跳舞 \obj{tiao4-tiao} \obj{wu3} / * 跳舞跳舞 \obj{tiao4wu3} \obj{tiao4wu3}).

4) Conjunction reduction. This criterion can only be applied to set apart coordinated phrases from coordinate compound words with a head in common (e.g. 火车 \obj{huo3che1} e 汽车 \obj{qi4che1} in (33) share the head  车 \obj{che1} `vehicle'). But the examples provided by the author(s) to argue against conjunction reduction with reduplicated verbs are completely different: the verbs do not have the head in common (exx. 34). I believe that this is not a reasonable test to argue for the wordhood of reduplicated verbs.

@@

The comparison with Parallel Verb Compounds and Serial Verb Constructions only serves to facilitate understanding
by contrasting the behaviors of different multi-verb constructions in Mandarin Chinese,
but this does not contribute to the arguments in any substantial way.
Due to the critics from the reviewers, this comparison is removed.

Cross-linguistically, verbal reduplication in Mandarin Chinese patterns more with morphological reduplication (below as reduplication) in other languages
than syntactic reduplication (below as repetition \citealt[31]{Gil2005}, \citealt[1--2]{Forza2016}).
\citet[35--36]{Gil2005} considers non-iconicity and having only two copies as sufficient but not necessary conditions for reduplication.
He further proposes building one intonational group as sufficient and necessary condition for reduplication (p. 36).
All three conditions are true for verbal reduplication in Mandarin Chinese.
% one intonational group \citep[154]{Sui2018}
\citet[9]{Forza2016} argues that the substantial difference between reduplication and repetition lies in the fact that only the former affects grammatical features such as aspect.
This is also true for verbal reduplication in Mandarin Chinese.

In sum, we maintain that verbal reduplication in Mandarin Chinese is better off analyzed as a morphological phenomenon.

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%%%%YL
\item
Sect. 3.3: I cannot understand the parallel with Mandarin verbal reduplication. The
author(s) say(s): ``The following section discusses previous literature which proposed a special
construction for the reduplication''. However, it becomes evident that the phenomenon under
examination is entirely different from Mandarin verbal reduplication. \citet{Ghomeshietal2004} analyze
a phenomenon which is well attested in world languages, even in those without productive
reduplication, i.e. contrastive focus reduplication/repetition, which involves the repetitions of
words and sometimes phrases (Oh, we re not LIVING-TOGETHER-living-together, \citealt[308]{Ghomeshietal2004}). Their function is “to focus the denotation of the reduplicated element on a more sharply delimited, more specialized, range” \citep[308]{Ghomeshietal2004}; for example, in ex. (47) cited by the author(s) SALAD-salad means green salad vs. salads in general. This has nothing to do with diminishing verbal reduplication in Mandarin. The authors' endeavor to apply the analysis proposed for contrastive focus reduplication to Mandarin verbal reduplication raises questions about its rationale (why? These two phenomena are fundamentally distinct and serve different linguistic functions). Consequently, attempting to employ the same analytical framework for both is problematic, and, indeed, the author(s) conclude(s) that: ``this approach fails to account for the similarities of the reduplication and other aspect markers in Mandarin Chinese''. This is precisely because contrastive focus repetition/reduplication is a different phenomenon with a different function, and Mandarin verbal reduplication cannot be analyzed in the same way. Furthermore, the author(s) suggest(s) that this approach ``[\ldots] also provides a formal account for the phonology of the reduplication''. However, contrastive focus reduplication/repetition generally does not involve morpho-phonological readjustment phenomena, which are typically found in reduplication. As a result, it cannot adequately account for phenomena such as the neutral tone of the reduplicant in the case of reduplication of monosyllabic verbs (\obj{kan4} > \obj{kan4} \obj{kan}).

@@

%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
Since the reviewer deemed it irrelevant, the section concerning \citet{Ghomeshietal2004} is removed.

%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
%% YL
\item p. 26, lines 24--25: ``The output reduplicates the phonology (phon) of the input verb with the possibility to have further phonological material in between. \etag indicates an underspecified list which could be empty or not''. However, it is not entirely clear what prevents phonological material other than \obj{yi} and \obj{le} to appear in between the reduplicated elements. This aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.

@@

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%% YL
\item
The proposed analysis appears to have limitations in explaining the constraints on verbs and the observed modifications at the Aktionsart level. How can one determine which verbs are exempt from the proposed lexical rule? The proposed rule does not seem to provide a clear prediction of which verbs are allowed and which are excluded from reduplication. Why only some states and achievements are allowed? The restrictions on the usage of the progressive with reduplicated verbs also remain unexplained.
%\item
The proposed analysis appears to have a descriptive rather than an explanatory power.
%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

%\textbf{Answer:} \itdopt{Stefan, say something. StMü: I would suggest to ignore this comment. }

%%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
As explained in point \ref{verbclass} on page \pageref{verbclass}, we propose that all verbs regardless of their basic Aktionsart can be reduplicated given suitable context.
The incompatibility with the progressive aspect marker is explained in the Semantics section.
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%% YL
\item
I would add tones to the \textit{pinyin} transcription.

%%%%
\textbf{Answer:} We added the tones.

@@

\textbf{Answer:}A footnote is added to the example to point this out: 
``As a reviewer comments, this example also involves the reduplication of V1 of a resultative compound. 
This runs counter to exiting literature on this subject which consistently maintains that resultative compounds are not amenable to reduplication''.

%%%%%%%%
\item
p. 5, exx. (11): I believe it would be useful to provide also an example illustrating that reduplicated verbs are incompatible with (post-verbal) for X-time adverbials.
%%%%

\textbf{Answer:} See the answer to point \ref{verbclass} on page \pageref{verbclass}.

%%%%
\item
p. 18, exx. (39b): to the best of my knowledge, the object can be placed before 一下 \obj{yixia} only in limited cases (pronouns and proper nouns).
%%%%%%%%%%%%%

@@

\noindent
\textbf{Answer:}
There are some examples from the corpus showing that not only pronouns and proper nouns can be placed before \obj{yi2} \obj{xia4} `once':
\ea%她看了他的脸一下。(CCL)
\gll \objex{ta1} \objex{kan4-le} \objex{ta1de} \objex{lian3} \objex{yi2} \objex{xia4}.\\
she look-\textsc{pfv} his face one time\\\jambox{(CCL)}
\glt `She took a look at his face.'

\ex%他没碰窗户，就看了玻璃一下，玻璃就烂了。(CCL)
\gll \objex{ta1} \ldots\, \objex{jiu4} \objex{kan4-le} \objex{bo1li} \objex{yi2} \objex{xia4}, \objex{bo1li} \objex{jiu4} \objex{lan4-le}.\\
he {} just look-\textsc{pfv} glass one time glass just break-\textsc{pfv}\\\jambox{(CCL)}
\glt `He just took a look at the glass and the glass just broke.'
\z
We think it has to do with the weight/length of the object, i.e. shorter objects can be placed before  \obj{yi2} \obj{xia4} `once' while longer ones cannot.
%This is not necessarily a syntactic constraint

Even if we accept that the object can be only be placed before  \obj{yi2} \obj{xia4} `once' in limited cases,
the fact that the object can be placed before  \obj{yi2} \obj{xia4} `once' in some cases but in no cases in between reduplication suggests there is a fundamental difference between the structure of the two phenomena.

%%%%%%%%%%%%%%
\item
p. 20, lines 28--31: ``\citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} assumed that the first
element in the reduplication is the actual verb, which resides under \textit{init} and \textit{proc}, and that the
second element is an aspect marker, which resides in the complement position of \textit{proc}, as it delimits
the process of the event''. Based on my understanding, these authors do not claim that the second
element serves as an aspect marker. They propose that the verb and the reduplicant are the spell-out
of two copies of the same lexical item within the \textit{v}P domain: the reduplicant is the lower copy, in
complement position, and serves as an event delimiter. In this analysis, reduplication affects the Aktionsart of the verb.

@@

%%%%%%%%%%%%%
\noindent
\textbf{Answer:} We reformulated as ``The second element is the copy of the verb, which resides in the complement position of proc and serves as an event delimiter.''

%%%%%%%%%%%%%
\item
p. 32, lines 28--34: ``Although these forms are generally considered unacceptable (\citealt[30]{LiThompson1981}; \citealt[275--276]{Hong1999}; \citealt[160]{BascianoMelloni2017}; \citealt[239]{YangWei2017}), \citet[269]{Fan1964} and \citet[143]{Sui2018} considered AB-yi-AB and AB-le -yi-AB to be possible, even though they both recognized that these two forms are rare.'' Given that these patterns were possible in previous stages of the language (see a.o. \citealt{BascianoMelloni2017}), these rare occurrences can be seen as relics of this usage.

@@

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:} A footnote is added to this sentence to point this out: 
``One reviewer suggests that given that AB-\obj{yi}-AB and AB-\obj{le}-\obj{yi}-AB were possible in previous stages of the language (see \citealt[15]{Zhang2000}, \citealt[160--161]{BascianoMelloni2017}), these rare occurrences can be seen as relics of this usage''.

%\itdopt{St.Mü.: Did you add a footnote or is this something to be done?}
%%%%%%%%%%%%%%%%%%%%%%
\end{enumerate}

\section{Reviewer 2}\label{sec:2}
\begin{enumerate}
\item
This paper presents an innovative analysis of verb reduplication in Mandarin Chinese, demonstrating
clarity and well-organized sections. To enhance clarity, I recommend providing a brief illustration for
technical terms like LTOP, catering to readers less familiar with them.

\textbf{Answer:} These terms will be explained in detail in point \ref{ltop} on page \pageref{ltop}.

\item
The authors employ various tests to assert that verb reduplication exhibits more word-like
characteristics than phrase-like, hence justifying its morphological classification. The subsequent
adoption of a Head-Driven Phrase Structure Grammar (HPSG) framework, integrating Minimal
Recursion Semantics (Copestake et al., 2005), presents advantages over prior analyses.

Despite these strengths, certain questions warrant attention. The primary concern revolves around
treating verb reduplication as morphological. The authors compare it with Parallel Verb Compound
(PVC) and Serial Verb Construction (SVC), asserting that verb reduplication aligns more closely with
SVC than PVC in tests like phrase extension, substitution, and conjunction reduction. However, the
choice of SVC over regular verb phrases as a point of comparison with PVC and verb reduplication
lacks clarity. While SVC passes these tests, it is crucial to note that regular verb phrases may not pass
some, e.g., separate modification of subparts within a constituent.

In light of this, concluding that verb reduplication is more word-like and less phrase-like is
questionable, as regular verb phrases encounter similar challenges. Therefore, it is crucial to
explicitly justify why SVC was chosen over regular verb phrases for this comparison. Providing such
clarification will strengthen the robustness of the paper's argumentation and render the conclusion
that verb reduplication should be morphological more convincing.

For additional comments, please refer to the attached PDF file.

### 2024-09-06 replies-reviews.tex

\textbf{Answer:}
Based on the suggestions by the reviewers and further literature research, the section on word vs. phrase is drastically revised.
The different syntactic behaviors of the reduplication and a VP are compared,
and we conclude that the behavior of the reduplication is compatible with a lexical analysis.
The comparisons with Parallel Verb Compounds and SVCs are not substantial to our arguments and are thus removed.
See the answer to Reviewer~\ref{sec:1}, point~\ref{morph} on page~\pageref{morph} for more details. 
%\itdopt{St.Mü.: This is the original review. We should say something about it. For example point to
%  explanations above or say that the issues will be taken up below when we discuss the reviewers
%  detailed comments.}

@@

%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
%% YL
\item
R2 comments on the following passage: A-\obj{kan4-kan4}

I am curious about the acceptability of this form `A-kan-kan.' For instance, phrases like `shuo-kan-kan' (`say-look-look') or `ting-kan-kan' (`listen-look-look') do not seem acceptable to me.

@@

\ea %我得听看看你的条件再说\ldots \jambox{(BCC)}
\gll \objex{wo3} \objex{dei3} \obj{ting1-kan4-kan4} \objex{ni3de} \objex{tiao2jian4} \objex{zai4} \objex{shuo1}\ldots\\
I have.to listen-look-look your condition then say\\\jambox{(BCC)}
\glt `I'll have to listen to your conditions first before talking about it/ deciding.'
\z

A statistical comparison of the acceptability and the productivity of A-\obj{kan4-kan4} among speakers of different varieties of Mandarin Chinese has to be left for future studies.

\item
R2 comments on the following passage: The current study will only focus on the AA, A-yi-A, A-le-A, A-le-yi-A, ABAB and
AB-le-AB forms of verbal reduplication in Mandarin Chinese. AA-kan, A-kan-kan,
AAB, A-yi-AB, A-le-AB will also be mentioned.

One of the key questions addressed in this paper pertains to whether verb reduplication is best understood as a morphological or a syntactic phenomenon. However, it's noteworthy that the forms emphasized in this paper are all instances of syntactic verb reduplication \citep{Xie2020}.

@@

\itdopt{St. Mü: Können wir das nicht auch AABB? Das ist gar nicht schwer. Ich habe das für
  adverbiale Adjektive bereits implementiert. Man muss nur PHON in zwei Teile \ibox{1} und \ibox{2}
  spalten und dann eben \ibox{1} $\oplus$ \ibox{1} $\oplus$ \ibox{2} $\oplus$ \ibox{2} als PHON-Wert
nehmen. Wenn das wichtig ist, können wir das noch machen. Oder wir machen eine Fußnote hin.}

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
%% YL
\item
R2 comments on the following passage: The meaning of the reduplication is not compositional, as it does
not mean that the event denoted by the verb happens twice or multiple times, but
rather that the event happens for a short duration and/or for low frequency. This
non-compositionality suggests that a reduplication is more word-like.

I have reservations about this argument.Typically, the meaning of a phrase is constructed in a compositional manner, meaning that the individual parts contribute to the overall meaning, or it remains transparent (e.g., \citealt{Schaefer2009}). When it comes to verb reduplication, determining whether or not the meaning is transparent\slash compositional might pose a challenge. On one hand, the core meaning of a verb often remains unaltered\slash transparent even with reduplication. On the other hand, verb reduplication does introduce additional nuances, such as delimitativeness. Additionally, the authors suggest that reduplication might be compositional if it expresses a `twice or multiple times' concept, yet non-compositional if it indicates a notion of short duration. Leaving aside the question of whether `compositional' can be interpreted in this manner, it remains noteworthy that that what prior studies identified as morphological verb reduplication (AABB form) does convey a sense of repetition (or say, multiple times) and can be considered compositional. In summary, whether or not verb reduplication is compositional remains unclear.

R2 comments on example (26).

@@

Example (26) was employed to demonstrate that verb reduplication can be modified by an adverb as a whole but cannot have a part of it modified. The authors utilize this observation to bolster the argument that verb reduplication is a morphological, not a syntactic phenomenon.

However, the issue at hand is that even a standard verb phrase cannot be modified in this manner. Consider the following examples, in which the phrase `dakai men' is a phrase rather than a word.

\ea
\gll ta qingsheng de dakai men.\\
       he  quietly    \textsc{de} open door\\
\glt      'He opened the door quietly.'
\z

\ea[*]{\gll ta dakai qingsheng de men.\\
         he open quietly       \textsc{de} door\\
\glt         'He opened the door quietly.'}
\z

@@

The key consideration here is that the unacceptability of (26b) and examples such as (2) may not hinge solely on whether part of it can be modified. Instead, it could be associated with the post-verbal placement of the adverb.

Consequently, it becomes challenging to use these examples as support for the argument that verb reduplication should be classified as a morphological rather than a syntactic phenomenon. This is because even regular verb phrases cannot be partially modified in the same manner.

%\textbf{Answer:} %Yes, this is true.

R2 comments on the following passage: Nothing can intervene between a Parallel Verb Compound and its subparts cannot be modified separately either (27).

@@

Examples (27) and (28) serve as illustrations to demonstrate the application of the ``Lexical Integrity Hypothesis'' in distinguishing PVC from SVC.

In reference to (25), it is explained that the Lexical Integrity Hypothesis posits that 'No
phrase-level rule may affect a proper subpart of a word.' However, it is noteworthy that the authors
employ le-insertion in (27) and (28), indicating that le- cannot be inserted into PVC but can be
inserted into SVC. This might suggest that the use of le-insertion in these examples could be
construed as a form of phrase-level operation, potentially conflicting with the author's perspective
of regarding `le' as a morphological process.

R2 comments on the following passage:  conjunction reduction does not seem to be possible.

@@

Regarding example (34), the conjunctive structures do not exhibit conjunction reduction, a phenomenon that typically requires a degree of overlap between two elements, as shown in (32). Example (34) presents a scenario where there is no overlap between the verb structures.

Moreover, in Mandarin, conjunctions can only be employed with nouns and not with verbs phrases or
clauses \citep{Schaefer2009}. If this holds true, it is less likely to observe conjunction reduction for
verb phrases. Consequently, it would be inappropriate to assert that verb reduplication is more
word-like and less phrase-like, as even regular verb phrases may encounter problems undergoing
conjunction reduction.

R2 comments on the following passage: Following the analyses above, it is clear that the reduplication failed all of the tests for phrasal status. In comparison, Parallel Verb Compounds failed all the tests as well, whereas SVCs passed all of them. This makes the behavior of the reduplication seem more similar to that of a Parallel Verb Compound than that of an SVC. Therefore, it seems more appropriate to assume reduplication to be a morphological process rather than a syntactic one.

@@

In Section 2.4, the authors asserted that verb reduplication is more phrase-like than word-like based on its similarities with Parallel Verb Compounds as apposed to Serial Verb Construction (SVC).

However, it is crucial to acknowledge that SVC has distinctive features, some of which diverge from those of a standard verb phrase. This raises a concern that a verb phrase might not successfully pass certain tests applicable to SVC, such as the ability for a constituent to be partially modified (A regular verb phrase like 'Verb + Object' cannot be partially modified by an adverb, while each verb in an SVC structure can be modified separately (28)). Therefore, when verb reduplication cannot be partially modified, asserting that it is less phrase-like solely on the basis of its differences from SVC might be inappropriate. This is because even a regular verb phrase faces limitations.

In light of this, it becomes essential to clarify why SVC, rather than regular verb phrases, was
chosen as a comparison to Parallel Verb Compounds. Such clarification would enhance the
persuasiveness of the tests presented in this section.

%%%%%%%%%%%%%%%%%%%
\textbf{Answer:} 
See the answer to Reviewer~\ref{sec:1}, point~\ref{morph} on page~\pageref{morph} for a detailed answer.

@@

%\itdopt{St. Mü.: We have numbers now due to enumerate. Please specify the point you are referring to exactly.}

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
%% YL
\item
R2 comments on the following passage: Third, idioms (43a) lose their idiomatic meaning when used with verbal classifiers (43b), but maintain their idiomatic meaning with reduplications (43c)

The reason for the loss of idiomatic meaning in (43b) but not in (43c) could be attributed to the
presence of the number `san' in (43b). If `san xia' is replaced with `yi xia,' which remains a
verbal classifier, the idiomatic meaning is perserved. In this case, there appears to be no
distinction between verbal classifier and reduplication.

@@

%%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer}:
It is not \obj{san1} \obj{xia4} `three times' that is special, but it is \obj{yi2} \obj{xia4} `once' that is special.
We can replace \obj{san1} `three' with any number above two,
and the distinction still exist.
But \obj{yi2} \obj{xia4} `once' has acquired a duration reading `for a little while' that is not available to the other event quantifiers formed by \obj{xia4}, which only have the `for X times' interpretation (\citealt[77]{Deng2013}, \citealt[16]{Zhang2000}).
We think \obj{liang3} \obj{xia4} `twice' is following this tendency, too.
In this case, it is easy to interpret \obj{yi1} \obj{xia4} and \obj{liang3} \obj{xia4} not as referring to the actual number of action taking place,
but as duration adverbials as a whole,
thus differing them from ``actual'' verbal classifier phrases with other numerals.
%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%% Stefan
\item
R2 comments on the following passage: They provided
22 the lexical rule (48) for reduplication in general, and further proposed \textit{redup-a-lr} and \textit{redup-v-lr} as subtypes of redup-type, as illustrated in (49) and (50) respectively.

It would enhance reader comprehension if the authors could provide a brief illustration of symbols
like HOOK, LTOP, IND, ARG, etc. This will aid readers in better grasping the authors' subsequent
proposals in Section 4.

\textbf{Answer:}\label{ltop}
\itdopt{Stefan}

\item
R2 comments on (57).

Perhaps PHON is missed in LEX-DTR of (57), even though PHON is empty in (57).

@@

\noindent
\textbf{Answer:} PHON is not missing. The constraints regarding PHON on the mother and the daughter are coming from
another constraint. A constraint that is a subtype in the hierarchy. The type
perfective-reduplication-lr in (51), which says that the PHON value of the daughter \ibox{1} appears
twice in the PHON value of the mother with some other material (\etag) between the two occurrences of \ibox{1}.
%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

\end{enumerate}

\section{Reviewer 3}

\begin{enumerate}
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%% YL
\item
In Page 2, the draft says that CCL corpus was explored in addition to the author(s)' intuition. I think this corpus-based method to bolster the acceptability judgments of the verbal reduplication expressions would be one of the merits in the current draft. The author(s) might be better to say more about why the corpus data was additionally explored and what was the findings from the corpus data (in comparison to the introspective judgments).

@@

\item
In the middle, the draft mentions the -bar derivation and be-prefixation in German. I understand the phenomenon has a similarity to verbal reduplication in Chinese. Yet, at a glance the German examples looked out-of-the-blue to me.

\textbf{Answer:} The German examples are used to illustrate the arguments that morphological processes can be productive and does not necessarily change the category or valency of the input.
To improve readability, English examples of ``-able'' derivation and ``-ed'' inflection are used instead now.

\item
The following paragraph looks terse to me. The author(s) want to provide more explanation about the four tests. In addition, the footnote 6 might be better to move into the body.
Duanmu (1998) and Schäfer (2009) proposed the following four tests to distinguish words from phrases
in Mandarin Chinese: semantic compositionality, phrasal extension, phrasal substitution and
conjunction reduction.

\textbf{Answer:} 
Based on the suggestions by the reviewers and further literature research, this section is drastically revised.
We now only use the tests of phrasal extension (or ``modification'' according to \citealt[32]{Dai1992}, \citeyear[117]{Dai1998})
and phrasal substitution (or ``expansion'' according to \citealt[33]{Dai1992}, \citeyear[117--120]{Dai1998}).
The explanations to the tests are simplified and illustrated with examples.
See the answer to Reviewer \ref{sec:1}, point \ref{morph} on page \pageref{morph} for more detail.
